Orientation Control System: Enhancing Aerial Maneuvers for Quadruped Robots

### 2023-01-04 mdpi2022roscia.tex
added python

\section{Results of Simulations}
\label{sec:simulations}
To validate our \gls{ocs}, we present three simulations on different scenarios. We want to test the capability of the proposed approach to: 
reject a disturbance when the robot is in the flight phase of a jump, damp trunk oscillations after the touch-down, 
and work in parallel with the joints of the legs to achieve a highly dynamic motion. 
All the simulations are performed using \MF{ROS \cite{quigley2009ros} together with Gazebo \cite{koenig2004design}. Physics related parameters are reported in Table \ref{tab:pys_param}.} The robot full dynamics is modeled with Pinocchio \cite{carpentier2019pinocchio}. The references for the joints of the legs are computed off-line using Crocoddyl \cite{mastalli2020crocoddyl} and tracked with a proportional-derivative joint controller. The \gls{ocs} is commanded to  track base orientation references using the control law introduced in Subsection \ref{subsec:control_law}.\footnote{The video with all the simulations is available at web link \url{https://www.dropbox.com/scl/fo/wevvl0zvfp8gofie6x7rw/h?dl=0&rlkey=pap76cr813a0skrvrxl7qgrb9}.}

>>>>

\section{Results of Simulations}
\label{sec:simulations}
To validate our \gls{ocs}, we present three simulations on different scenarios. We want to test the capability of the proposed approach to: 
reject a disturbance when the robot is in the flight phase of a jump, damp trunk oscillations after the touch-down, 
and work in parallel with the joints of the legs to achieve a highly dynamic motion. 
All the simulations are performed using \MF{ROS \cite{quigley2009ros} together with Gazebo \cite{koenig2004design}. Physics related parameters are reported in Table \ref{tab:pys_param}.} The robot full dynamics is modeled with Pinocchio \cite{carpentier2019pinocchio}. The references for the joints of the legs are computed off-line using Crocoddyl \cite{mastalli2020crocoddyl} and tracked with a proportional-derivative joint controller. The \gls{ocs} is commanded to  track base orientation references using the control law introduced in Subsection \ref{subsec:control_law} \MF{coded in Python}.\footnote{The video with all the simulations is available at web link \url{https://www.dropbox.com/scl/fo/wevvl0zvfp8gofie6x7rw/h?dl=0&rlkey=pap76cr813a0skrvrxl7qgrb9}.}
